Using best practices for forecasting biodiversity changes in breeding birds

### 2017-07-13 manuscript/draft.Rmd
Add Acknowledgments section

>>>>

## Acknowledgments

This research was supported by the Gordon and Betty Moore Foundation's
Data-Driven Discovery Initiative through Grant GBMF4563 to E.P. White. We thank
the developers and providers of the data and software that made this research
possible including: the PRISM Climate Group at Oregon State University, the
staff at USGS and volunteer citizen scientists associated with the North
American Breeding Bird Survey, NASA, the World Climate Research Programme's
Working Group on Coupled Modelling and its working groups, the
U.S. Department of Energy's Program for Climate Model Diagnosis and
Intercomparison, and the Global Organization for Earth System Science Portals.
